### 2017-02-23 paper.tex
fix width fault

\subsection{Accuracy of Application Identification }

\subsubsection{Testing data set}
Testing data set are mappings of flow attributes and ground truth (also called rules). This testing data set were generated by our system in our lab in National Tsing Hua University in Taiwan in 2016. We manually operated applications to generate traffic. After the system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on the testing data set. There are 14659 rules in total, and there are 137 applications if we view each platform version of an application as one application.
(提fig 1)

@@

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/nat_evaluation}
\caption{Multiple Table Performance Evaluation Scenario}
\label{fig:nat_evaluation}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/nat_evaluation_result}
\caption{Result of Multiple Table Performance Evaluation}
\label{fig:nat_evaluation_result}
\end{figure}

The single table framework implementation is easier than multiple table framework, but the multiple table framework is more flexible. To verify the efficacy of multiple table vCPE framework, this experiment use the NAT service to compare the throughput between single table vCPE and multiple table vCPE.
To begin with, an overview of the experiment environment illustrated in Fig. \ref{fig:nat_evaluation}.  In this experiment, the controller is Ryu SDN controller, and run on the Dell PowerEdge R630 Rack Server. The SDN switch employ Pica8 P-3290 switch. We used the tool that iPerf2.0 could generate the network traffic. The iPerf server would be set a public IP address. And iPerf client connect to the SDN switch that the controller would execute the NAT service on the single and multiple table vCPE framework.
We use the iPerf  to generate the UDP packets and send to server from client, and set the fixed value to bandwidth at 100Mbps. These experiments would use diffrent payload sizes to inspect their performances.
As shown in Fig. \ref{nat_evaluation_result}, the throughput value show that the performances of large packets such as 1024 bytes and 1470 bytes is better than small packets. Because the NAT service need to set the packet header field and small payload size would send more packets to server at the same time, the performance of larger packets is well. We can see that the throughput value of multiple table framework is close to single table framework. So we can realize the multiple table framework is more flexible than single table framework, and the performance is close to each other.

\subsection{Accuracy of Application Identification }
\subsubsection{Testing data set}
Testing data set are mappings of flow attributes and ground truth (also called rules). This testing data set were generated by our system in our lab in National Tsing Hua University in Taiwan in 2016. We manually operated applications to generate traffic. After the system generated rules, it exported them into a file, because we wanted to do 10-fold cross validation on the testing data set. There are 14659 rules in total, and there are 137 applications if we view each platform version of an application as one application.
(提fig 1)

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/classification_classifying}
\caption{Architecture of our application identification system in classifying phase}
\label{fig:classifcation_evaluation}
\end{figure}
